A practical guide for selecting the spectral photon flux density distribution of light for comparing photosynthetic rates of leaves grown under different spectral light environments

### 2016-08-14 Header.Rmd
誤字脱字程度。タイトルに悩みつつ 3098wordsでとりあえず。

output:
  pdf_document:
    latex_engine: xelatex
    fig_caption: TRUE
fontsize: 20pt
geometry: margin=1.2in
  # html_document:
  #   toc: TRUE
  #   depth: 3
  #   theme: sandstone
  #   self_contained: TRUE
  #   fig_caption: TRUE
  # word_document:
  #   toc: FALSE
  #   fig_caption: TRUE
---

@@

  The spectral photon flux density distributions (SPDs) of light during growth and for measurements do not only directly affect the net photosynthetic rate (*P*~n~), but also interacts on it.
  This paper summarizes a plausible mechanism of the interaction, some situations in which the interaction should be considered, and recommendations for selecting appropriate measuring light to evaluate photosynthesis.
  The *P*~n~ should be measured under *in situ* conditions, depending on the purpose of the study.
  For studies focusing on plant growth after measurements, *P*~n~ should be measured under the SPD of light that the plant will be subjected to.
  In retrospective studies aiming to elucidate the causes of differences among experimental groups, measurements should be made under the SPDs of the lights the plants were grown under.
  In descriptive studies, *P*~n~ should be evaluated under several SPDs of measuring light to understand the general photosynthetic characteristics of the leaves.
  The *P*~n~ under a single-pattern SPD of measuring light is only one aspect of the photosynthetic characteristics of a leaf.
  The obtained results must be discussed in relation to the SPD of measuring light so as not to make biased evaluations.

>>>>

output:
#   pdf_document:
#     latex_engine: xelatex
#     fig_caption: TRUE
# fontsize: 20pt
# geometry: margin=1.2in
  html_document:
    toc: TRUE
    depth: 3
    theme: sandstone
    self_contained: TRUE
    fig_caption: TRUE
  word_document:
    toc: FALSE
    fig_caption: TRUE
---

@@

  The spectral photon flux density distributions (SPDs) of light during growth and for measurements do not only directly affect the net photosynthetic rate (*P*~n~), but also interacts on it.
  This paper summarizes a plausible mechanism of the interaction, some situations in which the interaction should be considered, and recommendations for selecting appropriate measuring light to evaluate photosynthesis.
  The *P*~n~ should be measured under *in situ* conditions, depending on the purpose of the study.
  For prospective studies focusing on plant growth after measurements, *P*~n~ should be measured under the SPD of light that the plant will be subjected to.
  In retrospective studies aiming to elucidate the causes of differences among experimental groups, measurements should be made under the SPDs of the lights the plants were grown under.
  In descriptive studies, *P*~n~ should be evaluated under several SPDs of measuring light to understand the general photosynthetic characteristics of the leaves.
  The *P*~n~ under a single-pattern SPD of measuring light is only one aspect of the photosynthetic characteristics of a leaf.
  The obtained results must be discussed in relation to the SPD of measuring light so as not to make biased evaluations.

### 2016-08-14 Main.Rmd
誤字脱字程度。タイトルに悩みつつ 3098wordsでとりあえず。

  The two photosystems---PSII and PSI---represent different spectral light absorption distributions due to their different compositions of binding pigments, mainly chl *a* and chl *b*.
  Within the chlorophyll (chl) absorption band (approximately 350--750 nm), longer wavelengths of light (> 680--690 nm) are estimated to be preferentially absorbed by PSI, and PSI is drastically overexcited [Fig. 1; @Evans_Anderson1987BBA; @Hogewoning_et_al2012PC; @Wientjes_et_al2013BBA; @Laisk_et_al2014BBA].
  This is because only chl *a* can absorb longer wavelengths of light, and PSI contains more chl *a* than does PSII.
  In contrast, monochromatic light at shorter wavelengths (< 680--690 nm) is estimated to be preferentially absorbed by PSII, or evenly absorbed by both photosystems [Fig. 1; @Evans_Anderson1987BBA; @Hogewoning_et_al2012PC; @Wientjes_et_al2013BBA; @Laisk_et_al2014BBA].
  These wavelength dependencies of the excitation balance between PSII and PSI determine the excitation energy distribution (EED) under a given SPD of light.
  Light with a given SPD is sometimes categorized as either PSII- or PSI-light according to whether the excitation energy is preferentially distributed to PSII or PSI [e.g. @Chow_et_al1990PNAS; @Melis1991BBA; @Pfannschmidt_et_al2001JBC; @Fan_et_al2007BBA; @Dietzel_et_al2008FJ; @Pfannschmidt_et_al2009AB; @Dietzel_et_al2011PC; @Hogewoning_et_al2012PC].

@@

  Ideally, photosynthetic rates and related indices should be measured under *in situ* conditions.
  In prospective studies focusing on plant growth after measurements, the measurements should be made under the SPD of light that the plant will be subjected to.
  For instance, when evaluating plants grown under artificial lighting that will be transplanted [e.g. @Kozai2007POP], the measurements should be made under sunlight because the plants will be transferred to a greenhouse and cultivated under sunlight.
  However, the measurements under sunlight may be less reliable because of fluctations in the incident PPFD.
  In such cases, SPD-controllable light sources might be helpful [e.g. @Yano_Fujiwara2012PM; @Fujiwara_et_al2013Proc] to make *in situ* evaluations under PPFD-stable conditions and to ensure reproducibility and reliability of the results.
  In retrospective studies that aim to explain differences among experimental groups, the measurements should be made under the SPDs of light that the plants received during the treatments.
  For instance, when differences in dry weight between plants grown under white LEDs and those grown under fluorescent lamps are analyzed and *P*~n~ is used as an explanatory variable, the measurements should be made using the white LEDs for the plants grown under white LEDs and using the fluorescent lamps for those grown under fluorescent lamps.
  In both prospective and retrospective studies, these simple *in situ* measurements will eliminate the problems caused by the interaction between the growth and the measuring light.

@@

  The *P*~n~ under a single-pattern SPD of measuring light is only one aspect of the photosynthetic characteristics of a leaf.
  Therefore, the obtained results must be discussed in relation to the SPD of the measuring light.
  Photosynthesis should be evaluated under *in situ* conditions or multi-pattern SPDs of measuring light so that the evaluation is not biased by the interaction between the SPDs of the growth and measureing lights.
  Imitating the various SPDs of light incident on the leaf for *in situ* evaluation might be difficult or impossible for technical reasons.
  In addition, measuring the *P*~n~ under multi-pattern SPDs is time-, resource-, and labor-consuming.
  Although these two approaches might not always be used to evaluate leaf *P*~n~, the interaction should always be considered  to make circumspect conclusions.

@@

  We thank Dr Sander W. Hogewoning (Plant Lighting B.V., the Netherlands) for providing data of absorpbance spectra of photosystems.
  This work was supported by JSPS KAKENHI Grant Number 26·9372.

>>>>

  The two photosystems---PSII and PSI---represent different spectral light absorption distributions due to their different compositions of binding pigments, mainly chl *a* and chl *b*.
  Within the chlorophyll (chl) absorption band (approximately 350--750 nm), longer wavelengths of light (> 680--690 nm) are estimated to be preferentially absorbed by PSI, and PSI is drastically overexcited [Fig. 1; @Evans_Anderson1987BBA; @Hogewoning_et_al2012PC; @Wientjes_et_al2013BBA; @Laisk_et_al2014BBA].
  This is because only chl *a* can absorb longer wavelengths of light, and PSI contains more chl *a* than does PSII.
  In contrast, monochromatic light at shorter wavelengths (< 680--690 nm) is estimated to be preferentially absorbed by PSII, or evenly absorbed by both photosystems [Fig. 1; @Evans_Anderson1987BBA; @Hogewoning_et_al2012PC; @Wientjes_et_al2013BBA; @Laisk_et_al2014BBA].
  These wavelength dependencies of the excitation balance between PSII and PSI determine the excitation energy distribution (EED) under a given SPD of light.
  Light with a given SPD is sometimes categorized as either PSII- or PSI-light according to whether the excitation energy is preferentially distributed to PSII or PSI [e.g. @Chow_et_al1990PNAS; @Melis1991BBA; @Pfannschmidt_et_al2001JBC; @Dietzel_et_al2008FJ; @Pfannschmidt_et_al2009AB; @Dietzel_et_al2011PC; @Hogewoning_et_al2012PC].

@@

  Ideally, photosynthetic rates and related indices should be measured under *in situ* conditions.
  In prospective studies focusing on plant growth after measurements, the measurements should be made under the SPD of light that the plant will be subjected to.
  For instance, when evaluating plants grown under artificial lighting that will be transplanted [e.g. @Kozai2007POP], the measurements should be made under sunlight because the plants will be transferred to a greenhouse and cultivated under sunlight.
  However, the measurements under sunlight may be less reliable because of fluctuations in the incident PPFD.
  In such cases, SPD-controllable light sources might be helpful [e.g. @Yano_Fujiwara2012PM; @Fujiwara_et_al2013Proc] to make *in situ* evaluations under PPFD-stable conditions and to ensure reproducibility and reliability of the results.
  In retrospective studies that aim to explain differences among experimental groups, the measurements should be made under the SPDs of light that the plants received during the treatments.
  For instance, when differences in dry weight between plants grown under white LEDs and those grown under fluorescent lamps are analyzed and *P*~n~ is used as an explanatory variable, the measurements should be made using the white LEDs for the plants grown under white LEDs and using the fluorescent lamps for those grown under fluorescent lamps.
  In both prospective and retrospective studies, these simple *in situ* measurements will eliminate the problems caused by the interaction between the growth and the measuring light.

@@

  The *P*~n~ under a single-pattern SPD of measuring light is only one aspect of the photosynthetic characteristics of a leaf.
  Therefore, the obtained results must be discussed in relation to the SPD of the measuring light.
  Photosynthesis should be evaluated under *in situ* conditions or multi-pattern SPDs of measuring light so that the evaluation is not biased by the interaction between the SPDs of the growth and measuring lights.
  Imitating the various SPDs of light incident on the leaf for *in situ* evaluation might be difficult or impossible for technical reasons.
  In addition, measuring the *P*~n~ under multi-pattern SPDs is time-, resource-, and labor-consuming.
  Although these two approaches might not always be used to evaluate leaf *P*~n~, the interaction should always be considered  to make circumspect conclusions.

@@

  We thank Dr Sander W. Hogewoning (Plant Lighting B.V., the Netherlands) for providing data of absorbance spectra of photosystems.
  This work was supported by JSPS KAKENHI Grant Number 26·9372.
